---
title: "lab_7_git"
author: "Ben Edwards"
date: "11/13/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
gc_df <- read_csv("gc_df.csv")

```
We are asking; is there a significant difference in recommended gun control action for male and female respondents (should guns be easier, harder or the same difficulty to get)?

Are we wine tasting tomorrow?

Ben: Data wrangling and counts

```{r}

get_guns <- gc_df %>%
  filter(gender != "NA", make_get_guns != "NA") %>% 
  count(gender, make_get_guns) %>% 
  spread(make_get_guns, n) %>% 
  select(-gender)

rownames(get_guns) <- c("Female", "Male")
```

My name is Ilayda the collaborator and I'm going to be doing chi-square test for independence!
Don't forget to run!

We ask: "Is there a significant association between sex and opinion on whether guns should be more difficult, easier, or the same difficulty to get?"

```{r}

#Let's look at the actual proportions:

guns_prop <- prop.table(as.matrix(get_guns),1)  # 1 stands for margin over which I wanna calculate proportions. (e.g Easier/total female)

# Run chi-square test for independence



guns_x2 <- chisq.test(get_guns)

guns_x2

#reject the null
```

"Recommended government action on gun access differed significantly between male (n= ) and female(n= ) respondents ($\chi^2$(`r guns_x2$parameter`)= ...., p< 0.001). Notably, a much higher proportion of female respondents (57.4%) recommend making it more diffcult to get guns, compared to 40.4% for male respondents."





